\chapter{Chapter 5 - Besieged in the Chapel Ruins}

\begin{battle}{Besieged in the Chapel Ruins}
\begin{multicols}{2}

\battleinfo{rout}{6-10}{\Byleth, \Dimitri, \Claude, \Dimitri, \Balthus, \Linhardt, \Ashe, Aelfric}
\prep{
	\inventory{
		\battalion{
			\swap{\Hapi}{\Edelgard}
			\swap{\Yuri}{\Dimitri}
		}
	}
	\units{
		\remove{\Hapi, \Constance, \Edelgard, \Hilda}
	}
	\map{
		\Dimitrif
		\begin{itemize}
			\move{1D, 1R}
		\end{itemize}
		\Claudef
		\begin{itemize}
			\move{3U, 1L}
		\end{itemize}
	}
}

\begin{enumerate}
\turn{
	\Yurif \arrow{left}{2}
	\begin{itemize}
		\move{3L}
		\item Combat Arts: Foul Play \Claude\ \arrow{left}{1}
	\end{itemize}
	\Claudef
	\moveattack{3L, 2U}{Thief Leader}{2L with Silver Bow (29 Str) or Steel Bow+ (30 Str)}
	\movewait{2D}
	 \Bylethf
	 \movewait{2D, 2R}
	 \Ashef
 	 \movegambit{3L}{Retribution}{\Dimitri}{1L}
 	 \Dimitrif
 	 \moveattack{4D}{Foretress Knight}{1D}
 	 \movewait{4D}
 	 \Balthusf
 	 \moveattack{1D}{Bird}{1D with \textbf{Vajra Mushti}}
 	 \Linhardtf
 	 \movephysic{2D}{\Dimitri}{or anyone else if \Dimitri\ is healthy.}
 	 \item Aelfric:
 	 \movewait{3D, 1L}
}
\columnbreak
\turn{
	\Linhardtf
	\onlyphysic{\Dimitri}{}
	\Dimitrif
	\movegambit{1L}{Blaze}{Assassin}{1D}
	\movewait{1D, 1L}
	\Balthusf
	 \ifc{the \enemy{Bird} is still alive}{
		 \attack{Bird}{1D}
	 }
	 \ifc{the \enemy{Bird} is dead}{
	 	\move{4R, 1U}
	 	\wait
	 }
	 \Claudef
	 \begin{itemize}
	 	\move{6D}
	 	\item Dismount
	 	\attack{Enemy}{1U, 1R with Steel Bow+}
	\end{itemize}
	\Bylethf
	\moveattack{5R}{Fortress Knight}{2U}
	\movewait{1L}
}

\item The rest of the map is mostly improv. General Tips:
\begin{itemize}
\item If the two mages near the boss haven't moved, \Dimitri\ should try to lure exactly one of them.
\item \Dimitri/\Balthus\ should prioritize killing units with battalions.
\item Be careful though, the paladins in \Dimitri's area have Horseslayers. He won't get one-shotted, but it can still be iffy.
\item If the main lower area is almost cleared, then \Dimitri\ should go for the boss and Tempest Lance him. Then go north to help \Byleth.
\item \Byleth\ will very frequently get rattled, this is expected. Prioritize attacking \enemy{Fortress Knights}, since \Byleth\ can't one-round them without crits.
\item Make sure no enemy units get in range of \Linhardt/\Ashe/Aelfric, otherwise you're going to lose a bunch of time. This sometimes can't be avoided.
\item \Linhardt\ should typically stay in place and use Physic every turn on \Dimitri/\Byleth
\item A 6 turn is the turn count to aim for, but 7-10 is very possible depending on how unlucky you are.
\end{itemize}

\end{enumerate}

\end{multicols}

\end{battle}